Cumulative Score Plots Experiment 2

### 2019-12-04 Experiment_2/exp2_score_plots.Rmd
plots library fix

library(dplyr)
```

@@

```{r}
temp <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

>>>>

library(dplyr)
library(ggpubr)
```

@@

temp <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))
